COMPONENT ANALYSIS

### 2024-01-09 minos/testing/S7_comp_change_boxplot_child.Rmd
Didnt render properly on arc, moving to explicitly save the image we want

  p1 <- ggplot(df2, aes(x = Variable, y = Change, group = Variable, colour = Variable, fill = Variable)) +
    geom_boxplot(notch = FALSE) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    theme(legend.position = 'bottom',
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank())
  print(p1)
}

>>>>

  p1 <- ggplot(df2, aes(x = Variable, y = Change, group = Variable, colour = Variable, fill = Variable)) +
    geom_boxplot(notch = FALSE) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    theme(legend.position = 'bottom',
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank())
  print(p1)

  ggsave(filename = paste0('sccb_boxplot_', intervention, '_top10.png'),
         plot = p1,
         path = 'plots/')
}

### 2024-01-09 minos/testing/S7_comp_change_boxplot_livWage.Rmd
Didnt render properly on arc, moving to explicitly save the image we want

---
title: "TOP10 COMPONENT ANALYSIS - Living Wage"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

  p1 <- ggplot(df2, aes(x = Variable, y = Change, group = Variable, colour = Variable, fill = Variable)) +
    geom_boxplot(notch = FALSE) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    theme(legend.position = 'bottom',
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank())
  print(p1)
}

>>>>

---
title: "COMPONENT ANALYSIS - Living Wage"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

  p1 <- ggplot(df2, aes(x = Variable, y = Change, group = Variable, colour = Variable, fill = Variable)) +
    geom_boxplot(notch = FALSE) +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    theme(legend.position = 'bottom',
          axis.title.x = element_blank(),
          axis.text.x = element_blank(),
          axis.ticks.x = element_blank())
  print(p1)

  ggsave(filename = paste0('sccb_boxplot_', intervention, '.png'),
         plot = p1,
         path = 'plots/')
}

### 2024-01-09 minos/testing/S7_comp_change_child.Rmd
Didnt render properly on arc, moving to explicitly save the image we want

---
title: "TOP10 COMPONENT ANALYSIS - PovertyChild"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

out.path.batch <- here::here('output', 'SIPHER7')
intervention <- 'hhIncomePovertyLineChildUplift'

@@

```{r}
# select only top 10% of equivalent income increases
base.sub <- base.batch %>%
  select(pidp, time, equivalent_income) %>%
  rename(baseline = equivalent_income)

int.sub <- int.batch %>%
  select(pidp, time, equivalent_income) %>%
  rename(intervention = equivalent_income)

merged <- merge(x = base.sub,
                y = int.sub,
                by = c('pidp', 'time'))

rm(base.sub, int.sub)

top10p <- merged %>%
  mutate(diff = intervention - baseline) %>%
  group_by(pidp) %>%
  summarise(sum_diff = sum(diff)) %>%
  filter(sum_diff > quantile(sum_diff, .9))

rm(merged)

print(paste0('Top 10% of improvers: n = ', nrow(top10p)))

base.batch <- base.batch %>%
  filter(pidp %in% unique(top10p$pidp))
int.batch <- int.batch %>%
  filter(pidp %in% unique(top10p$pidp))

rm(top10p)
```

>>>>

---
title: "COMPONENT ANALYSIS"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

out.path.batch <- here::here('output', 'SIPHER7')
intervention <- 'hhIncomeChildUplift'

@@

```{r}
# # select only top 10% of equivalent income increases
# base.sub <- base.batch %>%
#   select(pidp, time, equivalent_income) %>%
#   rename(baseline = equivalent_income)
# 
# int.sub <- int.batch %>%
#   select(pidp, time, equivalent_income) %>%
#   rename(intervention = equivalent_income)
# 
# merged <- merge(x = base.sub,
#                 y = int.sub,
#                 by = c('pidp', 'time'))
# 
# rm(base.sub, int.sub)
# 
# top10p <- merged %>%
#   mutate(diff = intervention - baseline) %>%
#   group_by(pidp) %>%
#   summarise(sum_diff = sum(diff)) %>%
#   filter(sum_diff > quantile(sum_diff, .9))
# 
# rm(merged)
# 
# print(paste0('Top 10% of improvers: n = ', nrow(top10p)))
# 
# base.batch <- base.batch %>%
#   filter(pidp %in% unique(top10p$pidp))
# int.batch <- int.batch %>%
#   filter(pidp %in% unique(top10p$pidp))
# 
# rm(top10p)
```
